Optimal Algorithms for Dynamic Balanced Graph Partitioning

### 2020-05-15 paper/disc20clustering.tex
small tikz chnage

	\draw[dotted, shorten <= -6pt, shorten >= -6pt] (a4)  -- (a1);
	\draw [->,blue, shorten <= -5pt, shorten >= -2pt] (a4) -- (b2);

	%cluster 3
	\draw   (2*\x,0) -- (\w+2*\x,0) -- (\w+2*\x,40) -- (2*\x,40) -- cycle ;
	\draw    (2*\x,20) -- (\w+2*\x,20) ;
	% Text Node
	\draw (2*\x+8,10) node (b3)   {$b_{3}$};
	% Text Node
	\draw (2*\x+8,30) node (a2)   {$a_{2}$};
	\draw[dotted, shorten <= -4pt, shorten >= -3pt] (b2)  -- (b3);
	\draw [->,blue, shorten <= -5pt, shorten >= -2pt] (b2) -- (a2);

	%cluster 4
	\draw   (3*\x,0) -- (\w+3*\x,0) -- (\w+3*\x,40) -- (3*\x,40) -- cycle ;
	\draw    (3*\x,20) -- (\w+3*\x,20) ;
	% Text Node
	\draw (3*\x+8,10) node (b4)   {$b_{4}$};
	% Text Node
	\draw (3*\x+8,30) node (a3)   {$a_{3}$};
	\draw[dotted, shorten <= -4pt, shorten >= -3pt] (a2)  -- (a3);
	\draw [->,blue, shorten <= -5pt, shorten >= -2pt] (a2) -- (b4);

	\draw[dotted,  shorten <= -3pt, shorten >= -5pt]  (b4) to[out=-100,in=-80] (b1);
	% arrow
	\draw[->, blue,shorten <= -3pt, shorten >= -4pt]  (b4) 
	to [out=-108,in=-130, distance=17mm]  (a4);
	\end{tikzpicture}
\end{minipage}\hfill
%
\begin{minipage}[b]{.45\textwidth}
	\begin{tikzpicture}[x=0.8pt,y=0.75pt,yscale=-1.25,xscale=1.25]
	\useasboundingbox  (0mm,-5mm) rectangle (0mm,10mm);
%cluster 1
\def\x{30}
\def\w{15}
%Shape: Rectangle
\draw   (0,0) -- (15,0) -- (15,40) -- (0,40) -- cycle ;
%Straight Lines
\draw   (0,20) -- (15,20) ;
% Text Node
\draw (8,10) node (b1)  {$b_{1}$} ;
% Text Node
\draw (8,30) node (b4)   {$b_{4}$};

@@

%\section{Additional Figures}
%\begin{comment}
\begin{figure}[H]	\label{fig:timeline}
	\centering
\begin{tikzpicture}
\draw [->] (-10mm,0) -- (5,0);
\draw [dotted] (-13mm,0) -- (-10mm,0);

@@

\draw [] (5mm,2pt) -- (5mm,-2pt)
node [black,midway,below=0pt,xshift=1pt] {$t''$};
%% vertical arrow 
%\draw [->] (3mm,14pt) -- (4.4mm,4pt)
%node [black,midway,above=0pt,xshift=-4pt] {separation of  $\{u,w\}$};
%% vertical arrow 
%\draw [->] (30mm,-24pt) -- (26.5mm,-7pt)
%node [black,midway,below=0pt,xshift=5pt, yshift=-5pt] {separation of  $\{u,v\}$};
\end{tikzpicture}
\caption{
Illustration of the timeline used in the proof of Theorem \ref{thm:k=2}.
Requests in $R_t$  are only to  $\{u,w\}$ and $\{u,v\}$,
which  arrive  during the interval $(t'',t]$.
Similarly,
request in $R_{t'}$  are to $\{u,w\}$ and some other pair, irrelevant to the analysis.
Hence, requests to $\{u,w\}$ are included in at most two such sets,
which are $R_{t'}$ and $R_t$.
This is because their intervals overlap on $(t'',t']$, shown with red thick line.
}
\end{figure}
%\end{comment}

>>>>

	\draw[thick,dotted, shorten <= -6pt, shorten >= -6pt] (a4)  -- (a1);
	\draw [->,blue, shorten <= -5pt, shorten >= -2pt] (a4) -- (b2);

	%cluster 3
	\draw   (2*\x,0) -- (\w+2*\x,0) -- (\w+2*\x,40) -- (2*\x,40) -- cycle ;
	\draw    (2*\x,20) -- (\w+2*\x,20) ;
	% Text Node
	\draw (2*\x+8,10) node (b3)   {$b_{3}$};
	% Text Node
	\draw (2*\x+8,30) node (a2)   {$a_{2}$};
	\draw[thick,dotted, shorten <= -4pt, shorten >= -3pt] (b2)  -- (b3);
	\draw [->,blue, shorten <= -5pt, shorten >= -2pt] (b2) -- (a2);

	%cluster 4
	\draw   (3*\x,0) -- (\w+3*\x,0) -- (\w+3*\x,40) -- (3*\x,40) -- cycle ;
	\draw    (3*\x,20) -- (\w+3*\x,20) ;
	% Text Node
	\draw (3*\x+8,10) node (b4)   {$b_{4}$};
	% Text Node
	\draw (3*\x+8,30) node (a3)   {$a_{3}$};
	\draw[thick,dotted, shorten <= -4pt, shorten >= -3pt] (a2)  -- (a3);
	\draw [->,blue, shorten <= -5pt, shorten >= -2pt] (a2) -- (b4);

	\draw[thick, dotted,  shorten <= -3pt, shorten >= -5pt]  (b4) to[out=-100,in=-80] (b1);
	% arrow
	\draw[->, blue,shorten <= -3pt, shorten >= -4pt]  (b4) 
	to [out=-108,in=-130, distance=17mm]  (a4);
	\end{tikzpicture}
\end{minipage}\hfill
%
\begin{minipage}[b]{.45\textwidth}
	\begin{tikzpicture}[x=0.8pt,y=0.75pt,yscale=-1.25,xscale=1.25]
	\useasboundingbox  (0mm,-5mm) rectangle (0mm,10mm);
%cluster 1
\def\x{30}
\def\w{15}
%Shape: Rectangle
\draw   (0,0) -- (15,0) -- (15,40) -- (0,40) -- cycle ;
%Straight Lines
\draw   (0,20) -- (15,20) ;
% Text Node
\draw (8,10) node (b1)  {$b_{1}$} ;
% Text Node
\draw (8,30) node (b4)   {$b_{4}$};

@@

%\section{Additional Figures}
\begin{comment}
\begin{figure}[H]	\label{fig:timeline}
	\centering
\begin{tikzpicture}
\draw [->] (-10mm,0) -- (5,0);
\draw [dotted] (-13mm,0) -- (-10mm,0);

@@

\draw [] (5mm,2pt) -- (5mm,-2pt)
node [black,midway,below=0pt,xshift=1pt] {$t''$};
%% vertical arrow 
%\draw [->] (3mm,14pt) -- (4.4mm,4pt)
%node [black,midway,above=0pt,xshift=-4pt] {separation of  $\{u,w\}$};
%% vertical arrow 
%\draw [->] (30mm,-24pt) -- (26.5mm,-7pt)
%node [black,midway,below=0pt,xshift=5pt, yshift=-5pt] {separation of  $\{u,v\}$};
\end{tikzpicture}
\caption{
Illustration of the timeline used in the proof of Theorem \ref{thm:k=2}.
Requests in $R_t$  are only to  $\{u,w\}$ and $\{u,v\}$,
which  arrive  during the interval $(t'',t]$.
Similarly,
request in $R_{t'}$  are to $\{u,w\}$ and some other pair, irrelevant to the analysis.
Hence, requests to $\{u,w\}$ are included in at most two such sets,
which are $R_{t'}$ and $R_t$.
This is because their intervals overlap on $(t'',t']$, shown with red thick line.
}
\end{figure}
\end{comment}
